\documentclass[12pt]{article}
\usepackage{pdfpages}
\usepackage[colorlinks=true]{hyperref}
\parindent=0pt

\parskip=\bigskipamount
\begin{document}
\begin{center} Math 2710W: Transition to Advanced Math (W version)\\
Jeremy Teitelbaum \\ Fall Semester, 2020
\end{center}

{\bf Instructor}\\
Jeremy Teitelbaum \\
\href{mailto:jeremy.teitelbaum@uconn.edu}{email: jeremy.teitelbaum@uconn.edu} \\
\href{http://teitelbaum.math.uconn.edu}{UConn web page: http://teitelbaum.math.uconn.edu} \\
\href{http://jeremy9959.net}{Personal web page: http://jeremy9959.net} \\
\href{http://uconn-cmr.webex.com/meet/jet08013}{Webex office: http://uconn-cmr.webex.com/meet/jet08013} \\
Office hours: 2:00-3:30 p.m. Mondays and Wednesdays, or at other mutually convenient times.  

{\bf Course Description.} This course is an introduction to mathematical proof, with examples from
combinatorics, number theory, set theory, and calculus.  It is a ``W'' course so significant time
will be devoted to the proper use of mathematical notation and language.


{\bf Textbook:} {\it The Book of Proof}, by Richard Hammack.  This is an {\it open textbook} that is available
for download at \href{https://www.people.vcu.edu/~rhammack/BookOfProof}{Hammack's Website}. You can also purchase a paperback
version of the book if you wish, but that is not required. 

{\bf Prerequisites.} MATH 1132 or 1152. Cannot be taken for credit after passing MATH 2143, 3150, 3210, 3230, 3240, 3260, 3270, 3330, 3370 or 224. {\it Note that a grade of C or better in this course is required for the Mathematics major and is a prerequisite for many of the 3000 level courses in the department.}



{\bf Piazza.} I will be making use of the \href{https://piazza.com/class/kcp1cyt4u5r440}{Piazza}
web site to promote sharing of ideas and progress among the class members.
Questions about the course should be directed to the piazza site.  You can access piazza
through the Husky CT course for the class, but you should have received an email enrolling
you in the class and providing a direct link.

{\bf Class operation:} I plan to teach this online course through a combination of synchronous and asynchronous
methods.  {\bf Disclaimer:}  We are all adapting to the new world of the COVID pandemic.  I ask for your indulgence
as we get all of this working correctly, and reserve the right to make changes to this as the semester
progresses, depending on how it all works. If you have concerns or difficulties with the course
    mechanics, or the course material, PLEASE get in touch with me before things go too far!  
\begin{enumerate}
  \item I will provide video discussions of key topics from the syllabus and will expect you to watch those
    videos and do the assigned reading, and work on the assigned problems outside of class.
  \item Class periods will be devoted to small group discussion of problems
    and writing samples.  I have assigned each of you to a group of 3 or 4 people with a designated
    15 minute window during the class periods once a week.  The group assignments are available
    on \href{http://huckyct.uconn.edu}{HuskyCT}.  During these brief conferences we will discuss
    homework problems.  I will assign a selection of problems for these group discussions.
    {\bf NOTE: Participation in these discussions counts as $25\%$ of your grade in the course!}
\end{enumerate}

{\bf Assessment.}  Grades in this course will be based on the
following:
\begin{itemize}
\item A take-home midterm exam,  worth $25\%$ of the total grade.  This will be (tentatively)
  be distributed on October 12 with a due date of October 19.
\item A take-home final exam worth $40\%$ of the final grade.
\item You are required to attend and participate in the small group discussions.  Your active participation
  in these discussions, by doing the required prep work and contributing to the discussion, is worth
  $25\%$ of your course grade.
\item Online assessments and periodic writing assignments will contribute an additional $10\%$ of your grade.
\end{itemize}


\vfill\eject
\begin{center}

{\bf\Large Policy Statements}

\end{center}


{\bf Academic Integrity} 

Students are bound by the university's policies on academic integrity.

{\bf Students with Disabilities}

{\it Students with disabilities} should contact me as soon as
possible to discuss any accommodations needed during the semester due
to a documented disabilities.  If you have a documented disability for
which you wish to request academic accommodations and have not
contacted the Center for Students with Disabilities, please do so as
soon as possible.  The CSD is located in Wilbur Cross, Room 204 and
can be reached at (860) 486-2020 or at csd@uconn.edu.  Detailed
information regarding the process to request accommodations is
available on the CSD website at www.csd.uconn.edu.  

{\bf Policy Against Discrimination, Harassment and Inappropriate
Romantic Relationships}

The University is committed to maintaining an environment free of
discrimination or discriminatory harassment directed toward any person
or group within its community – students, employees, or visitors.
Academic and professional excellence can flourish only when each
member of our community is assured an atmosphere of mutual respect.
All members of the University community are responsible for the
maintenance of an academic and work environment in which people are
free to learn and work without fear of discrimination or
discriminatory harassment.  In addition, inappropriate Romantic
relationships can undermine the University’s mission when those in
positions of authority abuse or appear to abuse their authority.  To
that end, and in accordance with federal and state law, the University
prohibits discrimination and discriminatory harassment, as well as
inappropriate Romantic relationships, and such behavior will be met
with appropriate disciplinary action, up to and including dismissal
from the University.  More information is available at
http://policy.uconn.edu/?p=2884.

{\bf Sexual Assault Reporting Policy}

To protect the campus community, all non-confidential University
employees (including faculty) are required to report assaults they
witness or are told about to the Office of Diversity \& Equity under
the Sexual Assault Response Policy.  The University takes all reports
with the utmost seriousness.  Please be aware that while the
information you provide will remain private, it will not be
confidential and will be shared with University officials who can
help.  More information is available at
http://sexualviolence.uconn.edu/.


\end{document}


%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
